An Algorithmic Introduction to Lagrangian Coherent Structures

### 2014-01-13 main.tex
Update Bickley jet lambda-lines

Coherent Lagrangian vortices are associated with the strain tensor
\[
E_\lambda(\boldsymbol x_0) = \frac12 [C_{t_0}^t(\boldsymbol x_0) - \lambda^2 I]
\]
and curves uniformly stretched by the same factor $\lambda$ when advected by the flow from time $t_0$ to $t$ are closed trajectories of one of two explicit 
differential equations: 
\begin{equation}
\boldsymbol r' = \boldsymbol \eta_\pm(\boldsymbol r),
\label{eq:etafields}
\end{equation}
where
\begin{equation}
\boldsymbol \eta_\pm = \sqrt{\frac{\lambda_2 - \lambda^2}{\lambda_2 - \lambda_1}} \boldsymbol \xi_1 \pm \sqrt{\frac{\lambda^2 - \lambda_1}{\lambda_2 
- \lambda_1}} \boldsymbol \xi_2.
\label{eq:eta}
\end{equation}
In subsequent sections $\lambda = 1$ always. We call the curves associated with coherent Lagrangian vortices lambda-lines.

@@

>>>>

Coherent Lagrangian vortices are associated with the strain tensor
\[
E_\lambda(\boldsymbol x_0) = \frac12 [C_{t_0}^t(\boldsymbol x_0) - \lambda^2 I]
\]
and curves uniformly stretched by the same factor $\lambda$ when advected by the flow from time $t_0$ to $t$ are closed trajectories of one of two explicit 
differential equations: 
\begin{equation}
\boldsymbol r' = \boldsymbol \eta_\pm(\boldsymbol r),
\label{eq:etafields}
\end{equation}
where
\begin{equation}
\boldsymbol \eta_\pm = \sqrt{\frac{\lambda_2 - \lambda^2}{\lambda_2 - \lambda_1}} \boldsymbol \xi_1 \pm \sqrt{\frac{\lambda^2 - \lambda_1}{\lambda_2 
- \lambda_1}} \boldsymbol \xi_2.
\label{eq:eta}
\end{equation}
We call the curves associated with coherent Lagrangian vortices lambda-lines.

@@

The script used to analyse lambda-line LCS is given in Listing~\ref{lst:Bickley jet lambda lcs subdomain}. The script produces the data shown in Figure~\ref{fig:Bickley jet lambda lcs convergence}. Parameter values used may read from the script. It is worth pointing out that in order to obtain closed orbits, $\lambda = 0.995$; with $\lambda = 1$ no closed orbits are found.

\lstinputlisting[caption={Bickley jet script for lambda-line LCSs},label=lst:Bickley jet lambda lcs subdomain]{listings/bickley_jet/lambda_lcs_convergence_subdomain.m}

\begin{figure}[hbt]
  \centering
  \includegraphics[width=.7\textwidth]{graphics/bickley_jet/lambda_lcs_convergence_400}
\includegraphics[width=.7\textwidth]{graphics/bickley_jet/lambda_lcs_convergence_500}
\includegraphics[width=.7\textwidth]{graphics/bickley_jet/lambda_lcs_convergence_600}
  \caption{Bickley jet closed lambda-line at varying resolutions}
  \label{fig:Bickley jet lambda lcs convergence}
\end{figure}
